Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-01 p2/works-inverse.tex
Towards a new proof
New script to enumerate references

\begin{mydef}[$\worksmsign$, $\worksmeqsign$]
For two sets of sequences $\sqs{A}$ and $\sqs{B}$
we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
that is, if all sequences in $\sqs{B}$ work (do not break the filesystem)
on any filesystem all sequences in $\sqs{A}$ work on.
We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.

@@

\begin{mydef}[$\T$]
We use $\T$ and write $a\T$ to denote the canonical mapping of 
values, filesystems, commands and sequences to the
representatives of their $\typeeq$-equivalence class.
\begin{itemize}
\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T \whr S\in\sqs{A}\}$.
\end{itemize}
\end{mydef}

@@

\begin{mycor}
For any filesystem $\FS$ and command $\alpha$, 
$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
TODO needed?
\end{mycor}

@@

\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they break a filesystem (they are not defined):
\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
\end{mylem}
\begin{proof}
This is trivial if $\GS\T=\fsbroken$, so we assume it is not so.
Let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. The only remaining case therefore is where they have the same values
at all nodes except $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
$[\GS\T(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

We write ${S\T}^{-1}$ for the inverse of the sequence $S\T$, which consists of the inverses of the commands in $S\T$
in reverse order.
\end{mydef}
Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is undefined.

\begin{mylem}
For representative commands
\[ \cTxynv^{-1} = \cTyxnv. \]
TODO needed? -maybe for \cref{negneg_is_typeeq}
\end{mylem}

From the definitions we can clearly see that - TODO not used
\begin{mycor}\label{negneg_is_typeeq}
$\forall S: ({S\T}^{-1})^{-1} = S\T$.
\end{mycor}

>>>>

\begin{mydef}[$\worksmsign$, $\worksmeqsign$]\label{def_works}
For two sets of sequences $\sqs{A}$ and $\sqs{B}$
we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
that is, if all sequences in $\sqs{B}$ work (do not break the filesystem)
on any filesystem all sequences in $\sqs{A}$ work on.
We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.

@@

\begin{mydef}[$\T$]\label{def_typemapping}
We use $\T$ and write $a\T$ to denote the canonical mapping of 
values, filesystems, commands and sequences to the
representatives of their $\typeeq$-equivalence class.
\begin{itemize}
\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T \whr S\in\sqs{A}\}$.
\end{itemize}
\end{mydef}

@@

\begin{mycor}\label{cor_typemap_transitive}
For any filesystem $\FS$ and command $\alpha$, 
$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
TODO needed?
\end{mycor}

@@

% TODO \alpha \neq \cbrk
\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they break a filesystem (they are not defined):
\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
\end{mylem}
\begin{proof}
Let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. The only remaining case therefore is where they have the same values
at all nodes except $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
$[\GS\T(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

We write ${S\T}^{-1}$ for the inverse of the sequence $S\T$, which consists of the inverses of the commands in $S\T$
in reverse order.
\end{mydef}
Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is not defined.

% Some further observations:
% For representative commands \[ \cTxynv^{-1} = \cTyxnv. \]
% $\forall S: ({S\T}^{-1})^{-1} = S\T$.
